Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-13 mtjournal.tex
mari's suggested changes on intro and approach sections

In the following section (section~\ref{sec:approach}), we outline our
approach to including syntactic information in MT evaluation, by
describing a family of metrics. In section~\ref{sec:paradigm}, we
describe the implementation details and make explicit which dimensions
of this family of metrics we explore in this paper.
Section~\ref{sec:faexpts} examines the correlation of several members
of this family with human judgments of fluency and adequacy over a
corpus of sentence translations and selects a favorable member of the
family (EDPM) based on this comparison. Section~\ref{sec:hter1} compares
the correlation of EDPM with HTER over a corpus of document- and
sentence-level comparisons, and demonstrates that its correlation is
favorable to that of competitor measures BLEU and TER at both sentence
and document levels, regardless of source-language or genre.
Section~\ref{sec:hter2} uses the tuning components of the TERp tools
to explore the combination of these syntactic measures with other
TERp-based word-based measures. Finally, section~\ref{sec:conclusion}
concludes with some remarks on challenges and future work.

@@

This work explores a family of dependency pair match (DPM) measures
that are composed of precision and recall combinations over various
decompositions of a syntactic dependency tree. These measures are
extensions of the dependency-pair F measures found in
\inlinecite{roark06:sparseval,owczarzak07labelleddepseval}.  Rather than
comparing string sequences, as BLEU does with its $n$-gram precision,
this approach defers to a parser for an indication of the relevant
words that indicate more about its meaning --- in these
implementations, the head on which that word depends.  Each sentence
(both reference and hypothesis) is converted to a labeled syntactic
dependency tree and then relations from each tree are extracted and
compared.

@@

We may not completely trust the parser's best parse.  The parser
itself, if we use a probabilistic parser, can provide an $n$-best
parse list forest for the translation reference and translation
hypothesis. We use the probability statistics of the forest to compute
expected counts for each decomposition. Though this approach yields
partial counts, standard comparisons like precision and recall are
still valid, and using the expectations can help cope with both error
in the parser and ambiguity in the translations (reference and
hypothesis).

When multiple decomposition types used together, we may combine these
subscores in a variety of ways.  We may compute precision and recall
subscores for each decomposition separately, or, since the results of
each decomposition are of different types entirely, we may compute
them as members of one large bag for an even simpler F score.  These
two approaches are equivalent when only one decomposition type is
included.  For simplicity in presentation, we use the following
notation, where $dl$ and $lh$ represent the two kinds of
decompositions described above and $\mu_h$ represents a harmonic mean:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
Dependency-based SParseval and the \textbf{d} approach from
\inlinecite{owczarzak07labelleddepseval}, then, may
each be understood as $F[dlh]$, while the latter's \textbf{d\_var}
method may be understood as something close to $F[dl,lh]$.

Both of the combination methods above ($F[\cdot]$ and
$\mu_{PR}[\cdot]$) are ``naive'' combinations, in that they treat each
decomposition as equivalent to the next.  One further direction to
explore involves tuning (presumably on held-out data) the precision
and recall weights for each decomposition type for a later linear
combination.

@@

\section{Experimental paradigm}
\label{sec:paradigm}
In this section, we describe the details of the implementation and
experimental variables explored in the experiments presented here.

>>>>

In section~\ref{sec:approach}), we outline our
approach to including syntactic information in MT evaluation, by
describing a family of metrics. In section~\ref{sec:paradigm}, we
describe the implementation details and make explicit which dimensions
of this family of metrics we explore in this paper.
Section~\ref{sec:faexpts} examines the correlation of several members
of this family with human judgments of fluency and adequacy over a
corpus of sentence translations and selects a favorable member of the
family, Expected Dependency Pair Match (EDPM), based on this comparison. Section~\ref{sec:hter1} compares
the correlation of EDPM with HTER over a corpus of document- and
sentence-level comparisons, and demonstrates that its correlation is
favorable to that of competitor measures BLEU and TER at both sentence
and document levels, regardless of source-language or genre.
Section~\ref{sec:hter2} uses the tuning components of the TERp tools
to explore the combination of these syntactic measures with other
TERp word-based measures. Finally, section~\ref{sec:conclusion}
concludes with some remarks on challenges and future work.

@@

This work explores a family of dependency pair match (DPM) measures
that are composed of precision and recall combinations over various
decompositions of a syntactic dependency tree. These measures are
extensions of the dependency-pair F measures found in
\inlinecite{roark06:sparseval} and \inlinecite{owczarzak07labelleddepseval}.  Rather than
comparing string sequences, as BLEU does with its $n$-gram precision,
this approach defers to a parser for an indication of the relevant
word tuples associated with meaning --- in these
implementations, the head on which that word depends.  Each sentence
(both reference and hypothesis) is converted to a labeled syntactic
dependency tree and then relations from each tree are extracted and
compared.

@@

We may not completely trust the parser's best parse.  The parser
itself, if we use a probabilistic parser, can provide an $n$-best
parse list for the translation reference and translation
hypothesis. We use the probability statistics of the list to compute
expected counts for each decomposition. Though this approach yields
partial counts, standard comparisons like precision and recall are
still valid, and using the expectations can help cope with both error
in the parser and ambiguity in the translations (reference and
hypothesis).

When multiple decomposition types are used together, we may combine these
subscores in a variety of ways.  We may compute precision and recall
subscores for each decomposition separately, or, since the results of
each decomposition are of different types entirely, we may compute
them as members of one large bag for an even simpler F score.  These
two approaches are equivalent when only one decomposition type is
included.  For simplicity in presentation, we use the following
notation, where $dl$ and $lh$ represent the two kinds of
decompositions described above and $\mu_h$ represents a harmonic mean:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
Dependency-based SParseval and the \textbf{d} approach from
\inlinecite{owczarzak07labelleddepseval} may
each be understood as $F[dlh]$, while the latter's \textbf{d\_var}
method may be understood as something close to $F[dl,lh]$.

Both of the combination methods above ($F[\cdot]$ and
$\mu_{PR}[\cdot]$) are ``naive'' in that they treat each
component score as equivalent to the next.  One further direction to
explore involves tuning (presumably on held-out data) the precision
and recall weights for each decomposition type for a later linear
combination.

@@

\section{Experimental paradigm}
\label{sec:paradigm}
% In this section, we describe the details of the implementation and
% experimental variables explored in the experiments presented here.
